Neural Neural Textures Make Better Simulators ``I Can't Believe It's Not Real!''

### 2022-06-13 CORL/example.tex
Added commented equation to use parenthesized UV values
Turned (u,v) into uv and (r,g,b) into rgb. Also made neural neural texture and image translation sections good

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_beautiful.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		%
		%JUNE 12:
		%Don't say 4 main components; say 2 components and 2 losses
		%TODO: Try to use right-angled arrows
		%TODO: Use tau as a function
		%Copy paste the figure multiple times, deleting things
		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
		%Formulation doesnt mentino texture; just uvl inputs and final outputs
		%Always use function notation tau(u,v) instead of just tau (in figure as well) 
		%The arrow should be running through tau. It's not a variable its a function...
		%Rename 'B' to "N" for batch size
		%Figure 8: Align consistent with inconsistent and use all 5 green ones
		%
		This figure is an overview TRITON.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses.
		Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@

	These neural textures are represented implicitly by a neural network that maps UV values to RGB values.%, and are used to obtain projections $\pi$ from 3d scenes $s$.
	\begin{equation}
		\qquad \tau: (u,v) \in\real^2 \rightarrow (r,g,b) \in\real^3 % \eqand 
	\end{equation}

	Given a 3d UVL scene $s$, we obtain texture projection $\pi=\tau\toL(s)$ by applying $\tau\toL$ to every pixel $(u,v,l) \in s$ individually.
	Each pixel in the resulting projection $(r,g,b)\in\pi$ is the result of selecting a texture index $i$ based on the label value $l$, then applying $\tau_i$ to the $u,v$ values.
	\begin{equation}
		\pi=\tau\toL(s) \eqand (r,g,b) \in \pi = \tau_i(u,v)
	\end{equation}

@@

			% The neural texture applied to a particular scene pixel $(u,v,l) \in s$ is multiplexed by $l$, and the respective output pixel $(r,g,b) \in \pi = \tau_l(u,v)$. 
			% Texture projections $\pi$ are obatined by applying a set of $L$ different neural neural textures $\tau\toL$ to a UVL scene $s$ pixelwise.
			% [[IMPORTANT: THIS IS TECHNICALLY INCORRECT AS l IS A VALUE BETWEEN 0 and 1]]

			% where $i\in[1,L]\cap\mathbb{Z}$ is the rank of $l$
			% When applied to a UVL scene, it is applied to each $(u,v,l) \in s$ pixel individually where every pixel $(r,g,b) \in \pi = \tau$ 
			%What is it...then how do we use it...
			% (as the 2nd sentence)
			% Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
			% project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
			% 			Neural Neural Textures $\tau\toL(u,v)$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.

@@

	Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
	\begin{equation}
			\tau_i(uv) = 
			\
			M_i\left(\left[
				\sin f_1 uv, \ 
				\cos f_1 uv, \ 
				\sin f_2 uv, \ 
				\cos f_2 uv, \ 
				\dots \ 
				\sin f_{256} uv, \ 
				\cos f_{256} uv \ 
			\right]\right)
	\end{equation}
	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
	 $f_i uv$ represents their dot product, 
	%  $rgb$ represents a 3d color vector,
	 and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
	 $M_i: \real^{256} \rightarrow \real^3$.
	Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.

	%Squeeze this down - we don't need explanations for why, that can go in the appendix.
	In practice, we found that TRITON learns faster with fourier-feature textures than raster textures, as well as being smoother and less noisy. 
	% The trained fourier-feature textures also exhibit less noise than its raster counterparts. 
	% We think this is because they do not suffer as much. 
	% It cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high. 
	% Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.

@@

	Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
	\begin{equation}
		\ph=\Tab(\pis)\eqand\ppish=\Tba(p)
	\end{equation}
	$T$ is a variation of MUNIT~\cite{munit}, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.

	Our image translation module, $T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and we use a different image similarity metric. During inference however, this intermediate noise is removed and our image translation module is completely determinstic. Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.

	$T$ is a bidirectional image translation module, and has two translation directions. $\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).

>>>>

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_beautiful.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $N$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		%
		%JUNE 12:
		%Don't say 4 main components; say 2 components and 2 losses
		%TODO: Try to use right-angled arrows
		%TODO: Use tau as a function
		%Copy paste the figure multiple times, deleting things
		%Mention "Neural Neural Texture": Its a function mapping UV to RGB
		%Formulation doesnt mentino texture; just uvl inputs and final outputs
		%Always use function notation tauuv instead of just tau (in figure as well) 
		%The arrow should be running through tau. It's not a variable its a function...
		%Rename 'B' to "N" for batch size
		%Figure 8: Align consistent with inconsistent and use all 5 green ones
		%
		This figure is an overview TRITON.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses.
		Although $\pi\toN$ and $\ph\toN$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

@@

	These neural textures are represented implicitly by a neural network that maps UV values to RGB values.%, and are used to obtain projections $\pi$ from 3d scenes $s$.
	\begin{equation}
		\qquad \tau: uv \in\real^2 \rightarrow rgb \in\real^3 % \eqand 
	\end{equation}

	Given a 3d UVL scene $s$, we obtain texture projection $\pi=\tau\toL(s)$ by applying $\tau\toL$ to every scene pixel $uvl \in s$ individually.
	Each pixel in the resulting projection $rgb\in\pi$ is the result of selecting a texture index $i$ based on the rank of label value $l$, then applying $\tau_i$ to the $u,v$ values.
	\begin{equation}
		\pi=\tau\toL(s) \eqand rgb \in \pi = \tau_i(uv)
	\end{equation}

@@

			% The neural texture applied to a particular scene pixel $uvl \in s$ is multiplexed by $l$, and the respective output pixel $rgb \in \pi = \tau_luv$. 
			% Texture projections $\pi$ are obatined by applying a set of $L$ different neural neural textures $\tau\toL$ to a UVL scene $s$ pixelwise.
			% [[IMPORTANT: THIS IS TECHNICALLY INCORRECT AS l IS A VALUE BETWEEN 0 and 1]]

			% where $i\in[1,L]\cap\mathbb{Z}$ is the rank of $l$
			% When applied to a UVL scene, it is applied to each $uvl \in s$ pixel individually where every pixel $rgb \in \pi = \tau$ 
			%What is it...then how do we use it...
			% (as the 2nd sentence)
			% Given a 3D scene $s$, we apply $\tau\toL$ to each UV to obtain RGB surface values...
			% project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
			% 			Neural Neural Textures $\tau\toLuv$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we apply a function on their surface's UV values with neural textures $\tau\toL$ to obtain projection $\pi$.

@@

	% Each neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
	% Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
	% \begin{equation}
	% 		\tau_i(uv) = 
	% 		\
	% 		M_i\left(\left[
	% 			\sin \left( f_1     \cdot \left(u,v\right) \right) , \ 
	% 			\cos \left( f_1     \cdot \left(u,v\right) \right) , \ 
	% 			% \sin \left( f_2     \cdot \left(u,v\right) \right) , \ 
	% 			% \cos \left( f_2     \cdot \left(u,v\right) \right) , \ 
	% 			\dots \ 
	% 			\sin \left( f_{256} \cdot \left(u,v\right) \right) , \ 
	% 			\cos \left( f_{256} \cdot \left(u,v\right) \right)  \ 
	% 		\right]\right)
	% \end{equation}
	% where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
	%  $f_i uv$ represents their dot product, 
	% %  $rgb$ represents a 3d color vector,
	%  and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
	%  $M_i: \real^{256} \rightarrow \real^3$.
	% Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.

	Each neural neural texture $\tau_i$ is a function consisting of two components: a multi-layer perceptron $M_i$ and a static set of 256 random spatial frequencies $f_{1...256}$. 
	Given a two-dimensional $uv$ vector, the spatial frequencies are used to generate a high dimensional embedding used as input for the MLP.
	\begin{equation}
			\tau_i(uv) = 
			\
			M_i(
				\sin( f_1     uv  ) , \ 
				\cos( f_1     uv  ) , \ 
				\sin( f_2     uv  ) , \ 
				\cos( f_2     uv  ) , \ 
				\dots \ 
				\sin( f_{256} uv  ) , \ 
				\cos( f_{256} uv  )  \ 
			)
	\end{equation}
	where $uv$ and $f_i \in N_{ormal}(\mu=0,\ \sigma=10)$ are two dimensional vectors,
	 $f_i uv$ represents their dot product, 
	%  $rgb$ represents a 3d color vector,
	 and $M_i$ maps a $uv$ embedding to an $rgb$ color value:
	 $M_i: \real^{256} \rightarrow \real^3$.
	Note that there is nothing special about 256 or 10: these hyperparameter values just happen to work nicely.

	%Squeeze this down - we don't need explanations for why, that can go in the appendix.
	In practice, we found that TRITON learns faster with neural neural textures than raster neural textures. The generated textures are also smoother and less noisy. 
	% The trained fourier-feature textures also exhibit less noise than its raster counterparts. 
	% We think this is because they do not suffer as much. 
	% It cfrom aliasing artifacts in the UV maps, where the loss gradient might skip over pixels in texture-space when the UVL scene is zoomed out too far or raster resolution is too high. 
	% Case in point: if you have a raster texture with very high resolution, the loss gradient is less likely to be passed to a given texel because the chance that a given UV value in a scene will be rounded to that pixel's coordinates is very small.

@@

	% Our image translation module $T$ is bidirectional: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
	Our image translation module $T$ is a bidirectional: $\Tab$ translates sim to real (aka domain A to domain B), and $\Tba$ translates real to sim (aka domain B to domain A).
	\begin{equation}
		\ph=\Tab(\pis)  \eqand  \ppish=\Tba(p)
	\end{equation}

	$T$, is based on the image translation module used in \citep{surgical_video_translation}, which is a based on a variant \cite{surgical_image_translation} of MUNIT \cite{munit}. 
	$T$ uses the same network architectures as MUNIT, and also inherits its adversarial losses $\ell_{adv}$, cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
	The main differences between our image translation model and MUNIT are that our style code is fixed making it unimodal, noise is injected into the latent codes during training to prevent overfitting, and we use a different image similarity metric. 
	During inference however, this intermediate noise is removed and our image translation module is completely determinstic. 
	% Apart from these differences, our image translation module has the same loss formulations and generator/encoder/discriminator network architectures as MUNIT.
